My title

### 2024-03-16 paper/paper.qmd
updated qmd file

library(tidyverse)
library(palmerpenguins)
library(ggplot2)
library(rstanarm)
library(purrr)
library(kableExtra)

@@

@@

modelsummary::modelsummary(
  list(
    "First Model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

@@

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

@@

posterior_vs_prior(model_1) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

@@

>>>>

library(tidyverse)
library(palmerpenguins)
library(ggplot2)
library(rstanarm)
library(purrr)
library(kableExtra)
library(ggridges)

@@

```{r}
data |>
  ggplot(aes(x = date)) +
  geom_area(aes(y = healthcare_expenditure, fill = "Healthcare")) +
  #geom_area(aes(y = nondurable_expenditure, fill = "Non-durable goods")) +
  #geom_area(aes(y = durable_expenditure, fill = "Durable goods")) +
  #geom_area(aes(y = services_expenditure, fill = "Services")) +
  labs(
    x = "Date",
    y = "Expenditure by categories"
  ) +
  theme_minimal()
```

```{r}
#| label: fig-4
#| fig-cap: Relationship between wing length and w
#| echo: false
#| warning: false
#| message: false

data$date <- as.Date(data$date)

data_long <- reshape2::melt(data, id.vars = "date")

data_long |>
  ggplot( aes(x = date, y = value, fill = variable)) +
  geom_area() +
  labs(title = "Contribution of Expenditure Categories Over Time",
       x = "Date",
       y = "Expenditure",
       fill = "Expenditure Category") +
  theme_minimal()

data_long

@@

second_model <- 
  readRDS(file = here::here("models/model_2.rds"))

modelsummary::modelsummary(
  list(
    "First Model" = first_model,
    "Second Model" = second_model
  ),
  statistic = "mad",
  fmt = 2
)
```

@@

@@

posterior_vs_prior(model_1) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()

```{r}
#| eval: false
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior2
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(model_2) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(model_2) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

@@

plot(second_model, "trace")
